Hydras \& Co.

### 2022-04-13 doc/gaia-chapter.tex
fix typos

Here is a list of lemmas proved by rewriting from \HydrasLib version ( ~\href{../theories/html/hydras.Epsilon0.Hprime.html}{Epsilon0.Hprime} ).

@@

In \href{../theories/html/gaia_hydras.GHydra.html}%
{\texttt{gaia\_hydras.GHydra}}, we import a few theorem abouthydra battles (see
~\href{../theories/html/theories/html/hydras.Hydra.Hydra_Theorems.html}{Hydra.Hydra\_Theorems}).

>>>>

In the rest of this section, we prove a few lemmas  by rewriting from \HydrasLib version ( ~\href{../theories/html/hydras.Epsilon0.Hprime.html}{Epsilon0.Hprime} ).

@@

In \href{../theories/html/gaia_hydras.GHydra.html}%
{\texttt{gaia\_hydras.GHydra}}, we import a few theorem about hydra battles (see
~\href{../theories/html/theories/html/hydras.Hydra.Hydra_Theorems.html}{Hydra.Hydra\_Theorems}).
